Token-level author diarization using clustering of stylistic contexts

### 2017-05-30 paper/paper.tex

\citet{rosso-2016} divided PAN 2016 author diarization task into three subtasks. First subtask is traditionally called intrinsic plagiarism detection (IPD). The goal of this task is to find plagiariarized parts of a document in which at least $70\%$ of text is written by main author and the rest by one or more other authors. The term \textit{intrinsic} means that a decision whether plagiarized parts exist or not has to be made only by analysing a given document, without any comparisons with external sources. In the rest of the paper we refer to this subtask as a task \textit{a}.

@@

identity

>>>>

@@

id
